MLH1 Results Outline

### 2020-02-24 doc/Results.rmd
slight changes in formating

Thse are our prediction for the M3 glm (just straint) models based on the variation of the gwRR's

1. no difference in DOM strains (for SC lengths (CONFIRM IF THERE ARE DIFFERENECES FOR GWRR))

2. PWD > SKIVE > the rest

3. Msm > mol

@@

The skeletonized measures show that the general pattern holds for total SC and the high rec strains. However there are a few exceptions -However in the molf strain, there might be strain specific evolution--the mol subsp all have more SC skel

-the SKIVE are within dom and kaz level -- so why does SKIVE have intermediate CO proportions and gwRR

<24sep14_PWD_m1 is lower than the others, 5jul17_MSM_m1 is the low MSM>

@@

**The mouse means for the reduced bivalent datasets are not significantly different between the high and low rec strains (for the total pooled data) (ttest; short p = `r Q2short.biv_t.test_High.Low$p.value` and long p = `r Q2long.biv_t.test_High.Low$p.value`). (the summary of mouse averages for this subset of ) **

@@

I ran another model that used the single bivalents observations to predict the normalize foci position with fixed effects of chromosome length, subspecies, strian and the interaction effects.

**M.X. Linear Model** $$1CO \ Normalized \ Position ~=~ chromosomeLength * subsp * strain + \varepsilon $$

>>>>

<Thse are our prediction for the M3 glm (just straint) models based on the variation of the gwRR's
1. no difference in DOM strains (for SC lengths )
2. PWD > SKIVE > the rest
3. Msm > mol>

@@

The skeletonized measures show that the general pattern holds for total SC and the high rec strains. However there are a few exceptions.

<-the SKIVE are within dom and kaz level -- so why does SKIVE have intermediate CO proportions and gwRR>

<!--24sep14_PWD_m1 is lower than the others, 5jul17_MSM_m1 is the low MSM-->

@@

**The mouse means for the reduced bivalent datasets (short and long) are not significantly different between the high and low rec strains (for the total pooled data) (ttest; short p = `r Q2short.biv_t.test_High.Low$p.value` and long p = `r Q2long.biv_t.test_High.Low$p.value`).**

@@

<I ran another model that used the single bivalents observations to predict the normalize foci position with fixed effects of chromosome length, subspecies, strian and the interaction effects.

**M.X. Linear Model** $$1CO \ Normalized \ Position ~=~ chromosomeLength * subsp * strain + \varepsilon $$>
